### 2021-08-13 paper/paper.tex
library -> package

The design of \trixi was guided by extensibility, ease of use, and efficiency
(in this particular order). Thus, it is likely possible to make (some parts) even
faster at the cost of simplicity and readability. Nevertheless, \trixi is already quite
fast, even compared to mature high-performance open source software,
as described in detail in Section~\ref{sec:performance-comparison}. In this
section, we focus mostly on the first two goals.

@@

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are many (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. These codes can often be configured to a limited extent
by specifying compile time options or editing parameter files. In contrast, users of
\trixi do not need to compile anything or learn parameter file syntax. Instead, they can
just load the library and write their simulation setups in Julia. Scripts that describe
a simulation setup for \trixi are referred to as ``elixirs''. As of version
v0.3.55 (August 2021), \trixi comes with approximately 200 example elixirs. A basic elixir
looks as follows:

>>>>

The design of \trixi was guided by extensibility, ease of use, and efficiency
(in this particular order). Thus, it is likely possible to make some parts even
faster at the cost of simplicity and readability. Nevertheless, \trixi is already quite
fast, even compared to mature high-performance open source software,
as described in detail in Section~\ref{sec:performance-comparison}. In this
section, we focus mostly on the first two goals.

@@

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are many (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. These codes can often be configured to a limited extent
by specifying compile time options or editing parameter files. In contrast, users of
\trixi do not need to compile anything or learn parameter file syntax. Instead, they can
just load the package and write their simulation setups in Julia. Scripts that describe
a simulation setup for \trixi are referred to as ``elixirs''. As of version
v0.3.55 (August 2021), \trixi comes with approximately 200 example elixirs. A basic elixir
looks as follows:
